Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
level scaling start

>>>>

To show the level scaling in a particular tree, we only considered complete levels as the analysis from Equation \ref{eq:levelcost} only considers
complete levels. From Equation \ref{eq:levelcost}, the high order computational term (represented by MatMul) is constant per level, the lower order 
computational term (represented by NNLS) grows like $O(2^\ell)$, and the latency cost grows similarly like $O(2^\ell)$.

From Figure \ref{fig:seqlevelbreakdown}, the MatMul cost decreases slightly per level, which
